I am a title (RO SLAM Methods/Implementation Survey)

### 2018-01-26 Paper.tex
removed .txt and .bib from git ignore
lets try not to make any more change to the git ignore
Completed intialisations
Added intializations ans the seif part. Still need to redo paragraphs and add references.

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These processes are furthur  divided into delayed and undelayed initializations.
	\subsection{Delayed initializations}
	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application. Localization can be performed only once a accurate estimations of the beacons are made. There are several methods that achieve this. 
	\subsubsection{Trilateration}
	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
	\subsubsection{Particle filter}

	\cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.

>>>>

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These processes are furthur  divided into delayed and undelayed initializations.
	\subsection{Delayed/Offline initializations}
	These are the intialisations where  therobots moves around offline collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application. Localization can be performed only once a accurate estimations of the beacons are made. There are several methods that achieve this. There are several offline algorithms that perform localization such as the least squares approach in[5 of Active range only beacon lov=calisationi],a posed based ekf as mentioned in[8] , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below
	\subsubsection{Trilateration}
	[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique where a basic  circle intersection technique. The rings are drawn at different points of the robots path , where the radius of the rings depends on the strength of the received sginal from the beacon. This method of intilizatio is highly ambiguous as the rings can have more than 1 point of intersecting  or no points intersecting. %more paperes needed
	\subsubsection{Particle filter}
	This takes a more probabilistic approach to estimating the initial location of the beacons. As mentioned in[thrun particle filter paper] initially the entire space is represented by particles. These particles are resampled based on importance weights every iteration. Eventually the particle set converges to a accurate location of the beacons. Though this method of localization can be computationally expensive it is preferred where the noise involved is non Gaussian.

	\subsection{Undelayed/Online initializations}
	In this case the robot both initializes and localizes itself and the beacons as it moves.
	as mentioned in \cite{Caballero2010}. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.
